Security Metrics for the Android Ecosystem

### 2015-10-02 dastats.tex
./update.sh

\newcommand{\daOSMonthsOfData}{49}

@@

\newcommand{\daEndDate}{2015-07-19}

@@

\newcommand{\daNumManufacturers}{301}

@@

\newcommand{\daNumModels}{2\,740}
\newcommand{\daNumOperators}{1\,460}

@@

\newcommand{\daNumOSDevices}{20\,400}

@@

\newcommand{\daOSTotalDaysData}{1\,330\,000}
\newcommand{\daMeanInsecurityPercNominal}{87.7\%}
\newcommand{\daMeanInsecurityPerc}{$87.7 \pm 0.0\%$}
\newcommand{\daMeanInsecurityPercTwosfNominal}{88\%}
\newcommand{\daMeanInsecurityPercTwosf}{$88 \pm 0\%$}
\newcommand{\daMeanSecurityPercNominal}{12.3\%}
\newcommand{\daMeanSecurityPerc}{$12.3 \pm 0.0\%$}
\newcommand{\daMeanSecurityPercTwosfNominal}{12\%}
\newcommand{\daMeanSecurityPercTwosf}{$12 \pm 0\%$}
\newcommand{\daVulnFreeNominal}{0.123}
\newcommand{\daVulnFree}{$0.123 \pm 0.0$}
\newcommand{\daMeanOutstandingVulnerabilities}{$0.53 \pm 0.0$}
\newcommand{\daUpdatednessNominal}{0.0523}
\newcommand{\daUpdatedness}{$0.0523 \pm 0.0$}
\newcommand{\daUpdatednessPercNominal}{5.23\%}
\newcommand{\daUpdatednessPerc}{$5.23 \pm 0.0\%$}
\newcommand{\daUpdatednessPercTwosfNominal}{5.2\%}
\newcommand{\daUpdatednessPercTwosf}{$5.2 \pm 0.0\%$}
\newcommand{\daSecurityScoreNominal}{2.87}
\newcommand{\daSecurityScore}{$2.87 \pm 0.0$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{79.5\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$79.5 \pm 0.0\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{79\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$79 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{20.5\%}
\newcommand{\daCurrentMeanSecurityPerc}{$20.5 \pm 0.2\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{21\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$21 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.205}
\newcommand{\daCurrentVulnFree}{$0.205 \pm 0.002$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.119 \pm 0.0$}
\newcommand{\daCurrentUpdatednessNominal}{0.0561}
\newcommand{\daCurrentUpdatedness}{$0.0561 \pm 0.0016$}
\newcommand{\daCurrentUpdatednessPercNominal}{5.61\%}
\newcommand{\daCurrentUpdatednessPerc}{$5.61 \pm 0.16\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{5.6\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$5.6 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{3.81}
\newcommand{\daCurrentSecurityScore}{$3.81 \pm 0.0$}
\newcommand{\daDailyParticipationNominal}{896}
\newcommand{\daDailyParticipation}{$896 \pm 249$}
\newcommand{\daNumFullVersions}{1\,270}
\newcommand{\daNumSigFullVersions}{95}

@@

\newcommand{\daNumFullVersionUpdates}{4\,590}
\newcommand{\daNumOSVersionUpdates}{3\,900}
\newcommand{\daUpdatesPerYearNominal}{1.26}
\newcommand{\daUpdatesPerYear}{$1.26 \pm 0.01$}

@@

\newcommand{\daNumFullOnlyVersionUpdates}{677}
\newcommand{\daNumSecurityUpdates}{1\,250}
\newcommand{\daNumPossibleSecurityUpdates}{2\,300}
\newcommand{\daOSCurveFitParamFirst}{84.4}
\newcommand{\daOSCurveFitParamSecond}{\num{0.00285}}
\newcommand{\daOSCurveFitRMSE}{0.115}
\newcommand{\daOSCurvePolyRMSE}{0.115}
\newcommand{\daOSCurveSplineRMSE}{0.115}
\newcommand{\daOSCurveHalfDeployedYearsNominal}{0.897}
\newcommand{\daOSCurveHalfDeployedYears}{$0.897 \pm 0.252$}
\newcommand{\daOSCurveHalfDeployedNominal}{328}
\newcommand{\daOSCurveHalfDeployed}{$328 \pm 91$}
\newcommand{\daOSCurveFullDeployedYearsNominal}{3.11}
\newcommand{\daOSCurveFullDeployedYears}{$3.11 \pm 71$}
\newcommand{\daOSCurveFullDeployedNominal}{1\,140}
\newcommand{\daOSCurveFullDeployed}{$1\,140 \pm 260\,000$}
\newcommand{\daAPICurveFitParamFirst}{99.4}
\newcommand{\daAPICurveFitParamSecond}{\num{0.00285}}
\newcommand{\daAPICurveFitRMSE}{0.112}
\newcommand{\daAPICurvePolyRMSE}{0.112}
\newcommand{\daAPICurveSplineRMSE}{0.112}
\newcommand{\daAPICurveHalfDeployedYearsNominal}{0.939}
\newcommand{\daAPICurveHalfDeployedYears}{$0.939 \pm 0.244$}
\newcommand{\daAPICurveHalfDeployedNominal}{343}
\newcommand{\daAPICurveHalfDeployed}{$343 \pm 89$}
\newcommand{\daAPICurveFullDeployedYearsNominal}{3.15}
\newcommand{\daAPICurveFullDeployedYears}{$3.15 \pm 71$}
\newcommand{\daAPICurveFullDeployedNominal}{1\,150}
\newcommand{\daAPICurveFullDeployed}{$1\,150 \pm 260\,000$}
\newcommand{\daVulnAPKDuplicateFileOctoberPerc}{91.6\%}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.22 \pm 0.00$ & $0.33 \pm 0.00$ & $0.62 \pm 0.01$ & $3.97 \pm 0.02$ \\  Motorola & $0.18 \pm 0.00$ & $0.12 \pm 0.00$ & $0.71 \pm 0.02$ & $3.07 \pm 0.02$ \\  Samsung & $0.13 \pm 0.00$ & $0.04 \pm 0.00$ & $0.61 \pm 0.00$ & $2.75 \pm 0.00$ \\  Sony & $0.14 \pm 0.00$ & $0.19 \pm 0.00$ & $1.09 \pm 0.02$ & $2.63 \pm 0.02$ \\  HTC & $0.14 \pm 0.00$ & $0.10 \pm 0.00$ & $0.87 \pm 0.01$ & $2.63 \pm 0.02$ \\  asus & $0.20 \pm 0.00$ & $0.51 \pm 0.01$ & $6.01 \pm 0.07$ & $2.35 \pm 0.02$ \\  other & $0.06 \pm 0.00$ & $0.05 \pm 0.00$ & $1.04 \pm 0.01$ & $1.97 \pm 0.02$ \\  alps & $0.03 \pm 0.00$ & $0.19 \pm 0.01$ & $3.99 \pm 0.08$ & $0.80 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $5.00 \pm 0.05$ & $0.30 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.09 \pm 0.00$ & $6.00 \pm 0.08$ & $0.27 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table*}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{3.97}
\newcommand{\daSecScoreBestmanufacturerScore}{$3.97 \pm 0.0$}
\newcommand{\daSecScoreBestmanufacturerNumFullVersions}{135}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.272}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.272 \pm 0.007$}

@@

\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.50 \pm 0.00$ & $0.54 \pm 0.01$ & $1.53 \pm 0.04$ & $4.71 \pm 0.04$ \\  Nexus 4 & $0.30 \pm 0.00$ & $0.82 \pm 0.01$ & $6.06 \pm 0.09$ & $3.69 \pm 0.04$ \\  Nexus 7 & $0.26 \pm 0.00$ & $0.74 \pm 0.01$ & $5.92 \pm 0.09$ & $3.25 \pm 0.04$ \\  other & $0.10 \pm 0.00$ & $0.14 \pm 0.00$ & $0.53 \pm 0.00$ & $3.03 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & $0.38 \pm 0.02$ & $2.91 \pm 0.04$ \\  HTC Sensation & $0.35 \pm 0.00$ & $0.01 \pm 0.01$ & $1.57 \pm 0.05$ & $2.44 \pm 0.05$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & $1.23 \pm 0.02$ & $2.27 \pm 0.02$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.06$ & $1.74 \pm 0.07$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $2.52 \pm 0.05$ & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $1.79 \pm 0.06$ & $0.90 \pm 0.05$ \\  GT-I9300 & $0.13 \pm 0.00$ & $0.01 \pm 0.00$ & $6.23 \pm 0.04$ & $0.58 \pm 0.01$ \\  GT-I9505 & $0.03 \pm 0.00$ & $0.13 \pm 0.00$ & $6.82 \pm 0.07$ & $0.52 \pm 0.01$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $3.03 \pm 0.05$ & $0.28 \pm 0.03$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & $6.93 \pm 0.08$ & $0.24 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $11.00 \pm 0.12$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}

@@

\newcommand{\daSecScoreBestmodelScoreNominal}{4.71}
\newcommand{\daSecScoreBestmodelScore}{$4.71 \pm 0.0$}

@@

\newcommand{\daSecScoreWorstmodelScore}{$0.0001 \pm 0.0273$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline nexus & $0.39 \pm 0.00$ & $0.48 \pm 0.00$ & $0.56 \pm 0.01$ & $5.17 \pm 0.02$ \\  notnexus & $0.10 \pm 0.00$ & $0.02 \pm 0.00$ & $0.53 \pm 0.00$ & $2.70 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table*}}
\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.27 \pm 0.00$ & $0.12 \pm 0.00$ & $0.37 \pm 0.02$ & $3.87 \pm 0.03$ \\  T-Mobile & $0.21 \pm 0.00$ & $0.18 \pm 0.00$ & $0.40 \pm 0.01$ & $3.81 \pm 0.02$ \\  Orange & $0.22 \pm 0.00$ & $0.10 \pm 0.00$ & $0.36 \pm 0.02$ & $3.65 \pm 0.04$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & $0.43 \pm 0.02$ & $3.42 \pm 0.03$ \\  3 & $0.20 \pm 0.00$ & $0.09 \pm 0.00$ & $0.47 \pm 0.02$ & $3.39 \pm 0.03$ \\  Vodafone uk & $0.14 \pm 0.00$ & $0.13 \pm 0.00$ & $0.52 \pm 0.03$ & $3.17 \pm 0.04$ \\  AT\&T & $0.14 \pm 0.00$ & $0.08 \pm 0.00$ & $0.43 \pm 0.02$ & $3.13 \pm 0.02$ \\  unknown & $0.11 \pm 0.00$ & $0.20 \pm 0.00$ & $0.84 \pm 0.01$ & $2.88 \pm 0.02$ \\  Verizon & $0.19 \pm 0.00$ & $0.09 \pm 0.00$ & $0.82 \pm 0.02$ & $2.84 \pm 0.02$ \\  n Telenor & $0.04 \pm 0.00$ & $0.12 \pm 0.00$ & $1.21 \pm 0.02$ & $1.89 \pm 0.02$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & $1.47 \pm 0.03$ & $1.41 \pm 0.03$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $1.88 \pm 0.02$ & $0.94 \pm 0.01$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $2.07 \pm 0.04$ & $0.91 \pm 0.03$ \\  banglalink & $0.00 \pm 0.00$ & $0.03 \pm 0.00$ & $2.56 \pm 0.04$ & $0.54 \pm 0.02$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}

@@

\newcommand{\daSecScoreBestoperatorScoreNominal}{3.87}
\newcommand{\daSecScoreBestoperatorScore}{$3.87 \pm 0.0$}
\newcommand{\daSecScoreBestoperatorNumFullVersions}{100}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.536}
\newcommand{\daSecScoreWorstoperatorScore}{$0.536 \pm 0.018$}
\newcommand{\daSecScoreWorstoperatorNumFullVersions}{73}
\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & nexus \\ \hline equal & 0.0 & 0.0667 & 0.0 & 0.0 \\weight $m$ & 0.2 & 0.4 & 0.0714 & 0.0 \\$f$ & 0.4 & 0.667 & 0.5 & 0.0 \\weight $u$ & 0.4 & 0.0667 & 0.143 & 0.0 \\$m$ & 0.6 & 0.733 & 0.357 & 0.5 \\$u$ & 0.9 & 0.6 & 0.786 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & nexus \\ \hline $m$ & $-1.67 \pm 2.25$ & $-0.66 \pm 2.54$ & $-3.3 \pm 1.3$ & $-3.4 \pm 1.8$ \\weight $m$ & $-0.264 \pm 0.277$ & $-0.0991 \pm 0.321$ & $-0.461 \pm 0.167$ & $-0.488 \pm 0.217$ \\equal & $-0.108 \pm 0.062$ & $-0.0367 \pm 0.112$ & $-0.146 \pm 0.045$ & $-0.165 \pm 0.033$ \\weight $u$ & $-0.0608 \pm 0.122$ & $-0.0112 \pm 0.232$ & $0.0242 \pm 0.0808$ & $-0.00596 \pm 0.12$ \\$u$ & $0.367 \pm 1.61$ & $0.219 \pm 2.12$ & $1.55 \pm 0.94$ & $1.42 \pm 1.48$ \\$f$ & $0.975 \pm 0.564$ & $0.331 \pm 1.01$ & $1.31 \pm 0.41$ & $1.48 \pm 0.3$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}
\newcommand{\daGPAPICurveFitParamFirst}{80.8}
\newcommand{\daGPAPICurveFitParamSecond}{\num{0.00258}}
\newcommand{\daGPAPICurveFitRMSE}{0.179}
\newcommand{\daGPAPICurvePolyRMSE}{0.178}
\newcommand{\daGPAPICurveSplineRMSE}{0.178}
\newcommand{\daGPAPICurveHalfDeployedYearsNominal}{0.957}
\newcommand{\daGPAPICurveHalfDeployedYears}{$0.957 \pm 0.469$}

>>>>

\newcommand{\daOSMonthsOfData}{51}

@@

\newcommand{\daEndDate}{2015-09-22}

@@

\newcommand{\daNumManufacturers}{302}

@@

\newcommand{\daNumModels}{2\,770}
\newcommand{\daNumOperators}{1\,470}

@@

\newcommand{\daNumOSDevices}{20\,500}

@@

\newcommand{\daOSTotalDaysData}{1\,350\,000}
\newcommand{\daMeanInsecurityPercNominal}{87.3\%}
\newcommand{\daMeanInsecurityPerc}{$87.3 \pm 0.0\%$}
\newcommand{\daMeanInsecurityPercTwosfNominal}{87\%}
\newcommand{\daMeanInsecurityPercTwosf}{$87 \pm 0\%$}
\newcommand{\daMeanSecurityPercNominal}{12.7\%}
\newcommand{\daMeanSecurityPerc}{$12.7 \pm 0.0\%$}
\newcommand{\daMeanSecurityPercTwosfNominal}{13\%}
\newcommand{\daMeanSecurityPercTwosf}{$13 \pm 0\%$}
\newcommand{\daVulnFreeNominal}{0.127}
\newcommand{\daVulnFree}{$0.127 \pm 0.0$}
\newcommand{\daMeanOutstandingVulnerabilities}{$0.509 \pm 0.0$}
\newcommand{\daUpdatednessNominal}{0.0553}
\newcommand{\daUpdatedness}{$0.0553 \pm 0.0$}
\newcommand{\daUpdatednessPercNominal}{5.53\%}
\newcommand{\daUpdatednessPerc}{$5.53 \pm 0.0\%$}
\newcommand{\daUpdatednessPercTwosfNominal}{5.5\%}
\newcommand{\daUpdatednessPercTwosf}{$5.5 \pm 0.0\%$}
\newcommand{\daSecurityScoreNominal}{2.93}
\newcommand{\daSecurityScore}{$2.93 \pm 0.0$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{68.8\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$68.8 \pm 0.0\%$}
\newcommand{\daCurrentMeanInsecurityPercTwosfNominal}{69\%}
\newcommand{\daCurrentMeanInsecurityPercTwosf}{$69 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{31.2\%}
\newcommand{\daCurrentMeanSecurityPerc}{$31.2 \pm 0.2\%$}
\newcommand{\daCurrentMeanSecurityPercTwosfNominal}{31\%}
\newcommand{\daCurrentMeanSecurityPercTwosf}{$31 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.312}
\newcommand{\daCurrentVulnFree}{$0.312 \pm 0.002$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.0645 \pm 0.0$}
\newcommand{\daCurrentUpdatednessNominal}{0.0934}
\newcommand{\daCurrentUpdatedness}{$0.0934 \pm 0.0019$}
\newcommand{\daCurrentUpdatednessPercNominal}{9.34\%}
\newcommand{\daCurrentUpdatednessPerc}{$9.34 \pm 0.19\%$}
\newcommand{\daCurrentUpdatednessPercTwosfNominal}{9.3\%}
\newcommand{\daCurrentUpdatednessPercTwosf}{$9.3 \pm 0.0\%$}
\newcommand{\daCurrentSecurityScoreNominal}{4.43}
\newcommand{\daCurrentSecurityScore}{$4.43 \pm 0.0$}
\newcommand{\daDailyParticipationNominal}{872}
\newcommand{\daDailyParticipation}{$872 \pm 271$}
\newcommand{\daNumFullVersions}{1\,300}
\newcommand{\daNumSigFullVersions}{101}

@@

\newcommand{\daNumFullVersionUpdates}{4\,670}
\newcommand{\daNumOSVersionUpdates}{3\,940}
\newcommand{\daUpdatesPerYearNominal}{1.27}
\newcommand{\daUpdatesPerYear}{$1.27 \pm 0.01$}

@@

\newcommand{\daNumFullOnlyVersionUpdates}{724}
\newcommand{\daNumSecurityUpdates}{1\,270}
\newcommand{\daNumPossibleSecurityUpdates}{2\,310}
\newcommand{\daOSCurveFitParamFirst}{83.6}
\newcommand{\daOSCurveFitParamSecond}{\num{0.0028}}
\newcommand{\daOSCurveFitRMSE}{0.114}
\newcommand{\daOSCurvePolyRMSE}{0.114}
\newcommand{\daOSCurveSplineRMSE}{0.114}
\newcommand{\daOSCurveHalfDeployedYearsNominal}{0.908}
\newcommand{\daOSCurveHalfDeployedYears}{$0.908 \pm 0.254$}
\newcommand{\daOSCurveHalfDeployedNominal}{332}
\newcommand{\daOSCurveHalfDeployed}{$332 \pm 92$}
\newcommand{\daOSCurveFullDeployedYearsNominal}{3.16}
\newcommand{\daOSCurveFullDeployedYears}{$3.16 \pm 72$}
\newcommand{\daOSCurveFullDeployedNominal}{1\,150}
\newcommand{\daOSCurveFullDeployed}{$1\,150 \pm 265\,000$}
\newcommand{\daAPICurveFitParamFirst}{97.8}
\newcommand{\daAPICurveFitParamSecond}{\num{0.0028}}
\newcommand{\daAPICurveFitRMSE}{0.11}
\newcommand{\daAPICurvePolyRMSE}{0.111}
\newcommand{\daAPICurveSplineRMSE}{0.111}
\newcommand{\daAPICurveHalfDeployedYearsNominal}{0.946}
\newcommand{\daAPICurveHalfDeployedYears}{$0.946 \pm 0.244$}
\newcommand{\daAPICurveHalfDeployedNominal}{345}
\newcommand{\daAPICurveHalfDeployed}{$345 \pm 89$}
\newcommand{\daAPICurveFullDeployedYearsNominal}{3.2}
\newcommand{\daAPICurveFullDeployedYears}{$3.2 \pm 7$}
\newcommand{\daAPICurveFullDeployedNominal}{1\,170}
\newcommand{\daAPICurveFullDeployed}{$1\,170 \pm 265\,000$}
\newcommand{\daVulnAPKDuplicateFileOctoberPerc}{91.7\%}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.24 \pm 0.00$ & $0.34 \pm 0.00$ & $0.60 \pm 0.01$ & $4.11 \pm 0.02$ \\  Motorola & $0.19 \pm 0.00$ & $0.12 \pm 0.00$ & $0.71 \pm 0.02$ & $3.11 \pm 0.02$ \\  Samsung & $0.13 \pm 0.00$ & $0.04 \pm 0.00$ & $0.58 \pm 0.00$ & $2.80 \pm 0.00$ \\  Sony & $0.14 \pm 0.00$ & $0.19 \pm 0.00$ & $1.09 \pm 0.02$ & $2.66 \pm 0.02$ \\  HTC & $0.14 \pm 0.00$ & $0.10 \pm 0.00$ & $0.86 \pm 0.01$ & $2.65 \pm 0.02$ \\  asus & $0.21 \pm 0.00$ & $0.51 \pm 0.01$ & $6.01 \pm 0.07$ & $2.38 \pm 0.02$ \\  other & $0.06 \pm 0.00$ & $0.05 \pm 0.00$ & $1.00 \pm 0.01$ & $2.02 \pm 0.02$ \\  alps & $0.03 \pm 0.00$ & $0.19 \pm 0.01$ & $3.99 \pm 0.08$ & $0.80 \pm 0.02$ \\  Symphony & $0.00 \pm 0.00$ & $0.09 \pm 0.00$ & $5.00 \pm 0.05$ & $0.32 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.09 \pm 0.00$ & $6.00 \pm 0.08$ & $0.27 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table*}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{4.11}
\newcommand{\daSecScoreBestmanufacturerScore}{$4.11 \pm 0.0$}
\newcommand{\daSecScoreBestmanufacturerNumFullVersions}{142}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.273}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.273 \pm 0.007$}

@@

\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.50 \pm 0.00$ & $0.54 \pm 0.01$ & $1.53 \pm 0.04$ & $4.70 \pm 0.04$ \\  Nexus 4 & $0.33 \pm 0.00$ & $0.82 \pm 0.01$ & $6.06 \pm 0.09$ & $3.78 \pm 0.04$ \\  Nexus 7 & $0.27 \pm 0.00$ & $0.73 \pm 0.01$ & $5.92 \pm 0.09$ & $3.29 \pm 0.04$ \\  other & $0.10 \pm 0.00$ & $0.14 \pm 0.00$ & $0.51 \pm 0.00$ & $3.08 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & $0.38 \pm 0.02$ & $2.91 \pm 0.04$ \\  HTC Sensation & $0.35 \pm 0.00$ & $0.01 \pm 0.01$ & $1.57 \pm 0.05$ & $2.44 \pm 0.05$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & $1.23 \pm 0.02$ & $2.27 \pm 0.02$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.06$ & $1.74 \pm 0.07$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $2.52 \pm 0.05$ & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $1.79 \pm 0.06$ & $0.90 \pm 0.05$ \\  GT-I9505 & $0.06 \pm 0.00$ & $0.13 \pm 0.00$ & $6.82 \pm 0.07$ & $0.62 \pm 0.01$ \\  GT-I9300 & $0.13 \pm 0.00$ & $0.01 \pm 0.00$ & $6.23 \pm 0.04$ & $0.57 \pm 0.01$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $3.03 \pm 0.05$ & $0.28 \pm 0.03$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & $6.93 \pm 0.08$ & $0.24 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $11.00 \pm 0.12$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}

@@

\newcommand{\daSecScoreBestmodelScoreNominal}{4.7}
\newcommand{\daSecScoreBestmodelScore}{$4.7 \pm 0.0$}

@@

\newcommand{\daSecScoreWorstmodelScore}{$0.0001 \pm 0.0272$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline nexus & $0.40 \pm 0.00$ & $0.49 \pm 0.00$ & $0.55 \pm 0.01$ & $5.28 \pm 0.02$ \\  non-nexus & $0.11 \pm 0.00$ & $0.03 \pm 0.00$ & $0.51 \pm 0.00$ & $2.76 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table*}}
\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.28 \pm 0.00$ & $0.12 \pm 0.00$ & $0.37 \pm 0.02$ & $3.91 \pm 0.03$ \\  T-Mobile & $0.22 \pm 0.00$ & $0.19 \pm 0.00$ & $0.39 \pm 0.01$ & $3.87 \pm 0.02$ \\  Orange & $0.22 \pm 0.00$ & $0.10 \pm 0.00$ & $0.36 \pm 0.02$ & $3.64 \pm 0.04$ \\  3 & $0.22 \pm 0.00$ & $0.09 \pm 0.00$ & $0.47 \pm 0.02$ & $3.45 \pm 0.03$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & $0.43 \pm 0.02$ & $3.41 \pm 0.03$ \\  Vodafone uk & $0.14 \pm 0.00$ & $0.13 \pm 0.00$ & $0.52 \pm 0.03$ & $3.19 \pm 0.04$ \\  AT\&T & $0.15 \pm 0.00$ & $0.08 \pm 0.00$ & $0.43 \pm 0.02$ & $3.17 \pm 0.02$ \\  unknown & $0.12 \pm 0.00$ & $0.20 \pm 0.00$ & $0.80 \pm 0.01$ & $2.95 \pm 0.02$ \\  Verizon & $0.19 \pm 0.00$ & $0.09 \pm 0.00$ & $0.82 \pm 0.02$ & $2.86 \pm 0.02$ \\  n Telenor & $0.05 \pm 0.00$ & $0.12 \pm 0.00$ & $1.14 \pm 0.02$ & $2.01 \pm 0.02$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & $1.44 \pm 0.03$ & $1.45 \pm 0.03$ \\  Grameenphone & $0.01 \pm 0.00$ & $0.04 \pm 0.00$ & $1.66 \pm 0.02$ & $1.10 \pm 0.01$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $2.08 \pm 0.04$ & $0.91 \pm 0.03$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $2.55 \pm 0.04$ & $0.55 \pm 0.02$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}

@@

\newcommand{\daSecScoreBestoperatorScoreNominal}{3.91}
\newcommand{\daSecScoreBestoperatorScore}{$3.91 \pm 0.0$}
\newcommand{\daSecScoreBestoperatorNumFullVersions}{103}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.547}
\newcommand{\daSecScoreWorstoperatorScore}{$0.547 \pm 0.017$}
\newcommand{\daSecScoreWorstoperatorNumFullVersions}{75}
\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & nexus \\ \hline equal & 0.0 & 0.0 & 0.0714 & 0.0 \\weight $m$ & 0.2 & 0.333 & 0.214 & 0.0 \\weight $u$ & 0.2 & 0.0 & 0.143 & 0.0 \\$f$ & 0.3 & 0.733 & 0.357 & 0.0 \\$m$ & 0.6 & 0.733 & 0.357 & 0.5 \\$u$ & 0.9 & 0.667 & 0.786 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*}\small \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & nexus \\ \hline $m$ & $-1.67 \pm 2.26$ & $-0.65 \pm 2.56$ & $-3.34 \pm 1.27$ & $-3.4 \pm 1.9$ \\weight $m$ & $-0.263 \pm 0.278$ & $-0.0958 \pm 0.325$ & $-0.464 \pm 0.159$ & $-0.488 \pm 0.225$ \\equal & $-0.106 \pm 0.061$ & $-0.0343 \pm 0.111$ & $-0.145 \pm 0.043$ & $-0.164 \pm 0.035$ \\weight $u$ & $-0.0569 \pm 0.121$ & $-0.00706 \pm 0.225$ & $0.029 \pm 0.082$ & $-0.00391 \pm 0.12$ \\$u$ & $0.389 \pm 1.62$ & $0.238 \pm 2.09$ & $1.6 \pm 0.9$ & $1.44 \pm 1.51$ \\$f$ & $0.958 \pm 0.556$ & $0.309 \pm 1.0$ & $1.31 \pm 0.39$ & $1.48 \pm 0.32$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}
\newcommand{\daGPAPICurveFitParamFirst}{82.1}
\newcommand{\daGPAPICurveFitParamSecond}{\num{0.00257}}
\newcommand{\daGPAPICurveFitRMSE}{0.176}
\newcommand{\daGPAPICurvePolyRMSE}{0.176}
\newcommand{\daGPAPICurveSplineRMSE}{0.176}
\newcommand{\daGPAPICurveHalfDeployedYearsNominal}{0.964}
\newcommand{\daGPAPICurveHalfDeployedYears}{$0.964 \pm 0.462$}
\newcommand{\daGPAPICurveHalfDeployedNominal}{352}
